\subsection{Ideas and Technologies}
\subsubsection{Technologies to be Used}
After due consideration and taking into account the received requirements, the following technologies will possibly be used:
\begin{description}
	\item[In order to develop the back end of the system (API and Web Server):]\hfill
\begin{itemize}
	\item{ASP.NET MVC 5}\hfill\\
	%Description
	This will be used to develop the back-end of the system, using Microsoft's Visual 	Studio IDE.
	\item{ASP.NET Web API}\hfill\\
	This will form the back-bone of the API with which the rest system will interact (possibly hosted in the cloud).
	\item{C\#}\hfill\\
	Will be used in conjunction with .NET development.
\end{itemize}	

	\item[For the mobile app:]\hfill
	\begin{itemize}
		\item{Xamarin or Android Studio}\hfill\\
		The decision has yet to be made on whether the C\# Xamarin approach will be used or the traditional Java in Android Studio approach, to develop an Android application. One of these two will however reign supreme.
		\item{Open Source Libraries}
		Open Source Software such as GPSTracker by nickfox (github), can be used to track the phones location and this can then later be used to specify which screen the image should be cast to.
	\end{itemize}
	
\end{description}
	
\subsubsection{Implementation Ideas}
In order to develop the back end of the system [API]:\\
- One could do hosting in the cloud with the Micrsoft Azure hosting platform
- As students we would have access to many Microsoft products by registering at \href{http://www.dreamspark.com}{www.dreamspark.com}\\

The Repository Pattern as well as IoC (Inversion of Control) can be implemented. Another possible pattern that could be investigated is the Unit of Work pattern.

	
\subsubsection{Project Extension Ideas}
The following was considered as possible future extensions on the current project specifications:

\begin{itemize}
	\item{}
\end{itemize}