\subsection{Ideas and Technologies}
\subsubsection{Technologies to be Used}
After due consideration and taking into account the received requirements, the following technologies will possibly be used:
\begin{description}
	\item[In order to develop the back end of the system (API and Web Server):]\hfill
		\begin{itemize}
			\item{NodeJS}\hfill\\
			Node JS is a very popular web server hosting technology at this moment due 
			to its reliability, scalability and speed.
			\item{Express Framework}\hfill\\
			This framework will be used in conjunction with Node JS.
			\item{JavaScript front-end frameworks such as Bootstrap}\hfill\\
			This will be utilised for the GUI of the web server - simplistic, concise yet professional.
		\end{itemize}		
		
	\item[For the mobile app:]\hfill
	\begin{itemize}
		\item{Xamarin or Android Studio}\hfill\\
		The decision has yet to be made on whether the C\# Xamarin approach will be used or the traditional Java in Android Studio approach, to develop an Android application. One of these two will however reign supreme.
	
	
	\item{Near Field Communication (NFC)}\\
	NFC is a very important part of this project. Luckily it is not necessary to reinvent the wheel. NFCTools is a collection of libraries and tools for NFC in Java. The targeted devices are desktop Reader/Writer and Android smart phones. These libraries are open source and available for use in a project such as ours.
	\end{itemize}
	
\end{description}
	
\subsubsection{Implementation Ideas}
The project, from a development point of view, can be regarded as consisting of three individual parts.
\begin{enumerate}
	\item{Malware component}\\
Since malware should technically not be known to the user as being installed, some research will need to be done on how to hide an app from a user, as well as getting the malware installed on the user's device without the user's proper consent and knowledge.
	\item{Android App using NFC Component}\\
The most challenging part of this component will most probably be the NFC interaction and user identification.
	\item{Web Server / GUI Component}\\
In order for the android app to communicate with the server, some sort of hosting solution will need to be investigated. There are however many freely available service for Node hosting.
\end{enumerate}
	
\subsubsection{Project Extension Ideas}
The following was considered as possible future extensions on the current project specifications:

\begin{itemize}
	\item Direct upload to server\\
	Instead of the malware sending the voice recording by email, one could perhaps use a server using some form of encryption and a very specific communication protocol which would then deter authorities to send fake data to the receiver in order to catch the culprit. One could perhaps disguise it in the form of something that looks quite normal, like uploading it to DropBox.
	
\end{itemize}